Perceptual symbol grounding in \\Holographic memories

### 2016-11-08 papers/hrr-paper/paper.tex
Added capacity analysis and visual scene experiment.

\begin{document}
	%
	% paper title
	% Titles are generally capitalized except for words such as a, an, and, as,
	% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
	% not capitalized unless they are the first or last word of the title.
	% Linebreaks \\ can be used within to get better formatting as desired.
	% Do not put math or special symbols in the title.
	\title{Perceptual symbol grounding in \\holographic memories}

@@

	\begin{figure}
		\includegraphics[width=\columnwidth]{img/scalar-pre-perm-fft.png}
		\includegraphics[width=\columnwidth]{img/scalar-random-fft.png}
		\caption{Fourier space conversions of a Gaussian bell and a random vector.}
		\label{fft}
	\end{figure}

@@

	\subsection{Coordinate encoder}

	\subsection{String encoder}

	\section{Properties of SHM}

	- you can't extract the items memorized, number of them, you can just query
	- they are probabilistic
	- you can modify them online (no separate learning/probing phases)
	\subsection{Capacity}
	\subsubsection{SHM size vs. number of items}
	\subsubsection{Model of human forgetting}
	\subsubsection{Model of intentional forgetting}

	\subsection{Fan-out effect - multiple probing outputs}

	\subsection{Limitations}

	- introducing problem of lookup (symbol grounding)
	- solution using implicit encoding and decoding

@@

	\subsection{Visual object classification}
	- SIFT + label
	\subsection{Localization and mapping}
	- SIFT + location
\subsection{Symbolic scripting (holographic controllers)}

@@

	\subsection{Reinforcement learning}
	- sensory\_data + action + reward
	\subsection{Language understanding}
	- TensorFlow (role) + word = question answering
	\subsection{Implicit inductive reasoning}

>>>>

\begin{document}
	%
	% paper title
	% Titles are generally capitalized except for words such as a, an, and, as,
	% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
	% not capitalized unless they are the first or last word of the title.
	% Linebreaks \\ can be used within to get better formatting as desired.
	% Do not put math or special symbols in the title.
	\title{Perceptual symbol grounding in \\Holographic memories}

@@

	\begin{figure}
		\includegraphics[width=\columnwidth]{img/scalar-pre-perm-fft.png}
		\includegraphics[width=\columnwidth]{img/scalar-random-fft.png}
		\caption{Fourier analysis of 1D symbols: radial basis kernel (top row) and same dimensional vector randomly sampled from normal distribution (bottom row). It is obvious that latter is uniformly spread across the whole vector, while the former is concentrated around 2 boundary values leading to increased interference between multiple items stored one over another (when added in Fourier space).}
		\label{fft}
	\end{figure}

@@

	\section{Properties of holographic memories}

	Vector Symbolic Architectures in general have following properties:
	\begin{itemize}
		\item Number of items stored in a single memory vector is not known based only on it's content.
		\item Existence of item in memory cannot be explicitly checked. The closest equivalent is probing the memory for item of interest and comparing similarity of decoding result to anything meaningful.
		\item Chances of successful recall depend on the actual data stored.
		\item Memories can be changed in online fashion. There is no need to recreate memories from scratch - symbols can be appended to or removed from (if presents) already existing memory vectors.
	\end{itemize}

	\subsection{Capacity}

	As done by Plate et. al. in original HRR paper\cite{Plate:1995:HolographicReducedRepresentations} we have tested memory capacity in terms of accuracy of successful recall for variable number of bound pairs. Results are show in figure \ref{fig:capacity}.

		\begin{figure}[th!]
			\center
			\includegraphics[width=0.8\columnwidth]{img/capacity.png}
			\caption{Memory capacity analysis for storing variable number of pair associations in a single memory vector. Different lines show vector length, while horizontal axis shows number of pairs and vertical axis accuracy of successful recall.}
			\label{fig:capacity}
		\end{figure}

	As we can see, a 512 element vector starts decreasing accuracy of recall after 10 pairs stored in a single memory block. A 4096 and 8192 element vectors can almost perfectly recall 20 associated pairs, which matches the results of Plate using lookup table and cleanup process. As we can see, newly introduced perceptual symbol grounding did not have significant effect on memory capacity.

@@

	\subsection{Visual short term memory and top-down attention model}

	In this experiment a system is given a monocular stream as an input. An arbitrary algorithm is used to perform object detection and recognition, resulting in number of 2D coordinates associated with respective object names (figure \ref{fig:object-detection}). Object names are strings and are encoded as random vectors of length N, sampled from normal distribution (figure \ref{fig:encoding-object}). Locations of object in image plane are 2D coordinates $(x,y)$ and they are perceptually grounded symbols (figure \ref{fig:encoding-coord}).

	\begin{figure}[th!]
		\center
		\begin{subfigure}{0.8\columnwidth}
			\includegraphics[width=\columnwidth]{img/map_original.jpg}
			\caption{Original scene and set of detected objects}
			\label{fig:object-detection}
		\end{subfigure}

		\begin{subfigure}{0.45\columnwidth}
			\center
			\includegraphics[width=\linewidth]{img/coord_example_1.png}
			\caption{Encoding of (x,y) location of an object}
			\label{fig:encoding-coord}
		\end{subfigure}
		\begin{subfigure}{0.45\columnwidth}
			\center
			\includegraphics[width=\linewidth]{img/coord_example_2.png}
			\caption{Encoding of an object ID as randomly sampled vector}
			\label{fig:encoding-object}
		\end{subfigure}

				\begin{subfigure}{0.8\columnwidth}
					\center
					\includegraphics[width=\linewidth]{img/coord_example_3.png}
					\caption{Encoding of the complete visual scene, containing information about all 7 objects and their locations}
					\label{fig:encoding-scene}
				\end{subfigure}

			\begin{subfigure}{0.45\columnwidth}
				\center
				\includegraphics[width=\linewidth]{img/probe_for_mug.png}
				\caption{Probing for "mug" returns location probability mug}
				\label{fig:probing-single}
			\end{subfigure}
			\begin{subfigure}{0.45\columnwidth}
				\center
				\includegraphics[width=\linewidth]{img/probe_for_pen.png}
				\caption{Probing for "pen" return mixture of Gaussians}
				\label{fig:probing-double}
			\end{subfigure}

		\caption{Representation of visual scene in short term symbolic memory. }
		\label{fig:visual-scene-exp}
	\end{figure}

	\subsection{Localization and mapping}
	- TBD

\subsection{Symbolic scripting (holographic controllers)}

@@
